Do expert pianists adapt their pedagogical demonstrations to novices' skills?

### 2022-12-01 paper/manuscript.Rmd
update figures
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r ioi-plot, include = FALSE}
ioi_all_plot <- ggplot(ioi[Category != "baseline"], aes(x = Articulation, y = Mean, color = Dynamics)) +
  geom_boxplot(outlier.shape = NA, position = position_dodge2(preserve = "single")) +
  geom_hline(yintercept = 300, linetype = "dashed") +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) + labs(y = "IOI (ms)", title = "IOI") + scale_y_continuous(breaks = seq(250, 300, 10), limits = c(250, 300)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

@@

```{r kot-plot, include = FALSE}
leg_all_plot <- ggplot(kot[Subcomponent1 == "Legato" & Category != "baseline"], aes(x = Articulation, y = Mean, color = Dynamics)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KOT (ms)", title = "KOT - Legato") + scale_y_continuous(breaks = seq(-10, 120, 40)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

sta_all_plot <- ggplot(kot[Subcomponent1 == "Staccato" & Category != "baseline"], aes(x = Articulation, y = Mean, color = Dynamics)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KOT (ms)", title = "KOT - Staccato") + scale_y_continuous(breaks = seq(-310, -170, 40)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

@@

```{r vel-plot, include = FALSE}
for_all_plot <- ggplot(vel[Subcomponent2 == "Forte" & Category != "baseline"], aes(x = Dynamics, y = Mean, color = Articulation)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KV (0-127)", title = "KV - Forte") + scale_y_continuous(breaks = seq(60, 110, 10)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

pia_all_plot <- ggplot(vel[Subcomponent2 == "Piano" & Category != "baseline"], aes(x = Dynamics, y = Mean, color = Articulation)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KV (0-127)", title = "KV - Piano") + scale_y_continuous(breaks = seq(50, 70, 10)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

@@

```{r vel-diff-plot, include = FALSE}
ftop_all_plot <- ggplot(vel_diff[Subcomponent2 == "FtoP" & Category != "baseline"], aes(x = Dynamics, y = Mean, color = Articulation)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KV Difference (-127-127)", title = "KV Difference - FtoP") + scale_y_continuous(breaks = seq(-35, 0, 10)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

ptof_all_plot <- ggplot(vel_diff[Subcomponent2 == "PtoF" & Category != "baseline"], aes(x = Dynamics, y = Mean, color = Articulation)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KV Difference (-127-127)", title = "KV Difference - PtoP") + scale_y_continuous(breaks = seq(-5, 45, 10)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

@@

```{r ioi-bl-plot, include = FALSE}
ioi_ca_plot <- ggplot(ioi[Category == "none" | Category == "both" | Category == "baseline"], aes(x = factor(Category, level = c("baseline", "none", "both")), y = Mean)) +
  geom_boxplot(outlier.shape = NA, position = position_dodge2(preserve = "single")) +
  geom_hline(yintercept = 300, linetype = "dashed") + scale_y_continuous(breaks = seq(250, 300, 10), limits = c(250, 300)) +
  geom_jitter(width = 0.15, alpha = 0.5) + labs(x = "Category", y = "IOI (ms)", title = "IOI") +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

@@

```{r kot-bl-plot, include = FALSE}
leg_ca_plot <- ggplot(kot[Subcomponent1 == "Legato" & Category == "baseline" | Subcomponent1 == "Legato" & Category == "both" | Subcomponent1 == "Legato" & Category == "dyn_only"], aes(x = factor(Category, level = c("baseline", "dyn_only", "both")), y = Mean)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.15, alpha = 0.5) +
  labs(x = "Category", y = "KOT (ms)", title = "KOT - Legato") + scale_y_continuous(breaks = seq(-10, 120, 40)) +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

sta_ca_plot <- ggplot(kot[Subcomponent1 == "Staccato" & Category == "baseline" | Subcomponent1 == "Staccato" & Category == "both" | Subcomponent1 == "Staccato" & Category == "dyn_only"], aes(x = factor(Category, level = c("baseline", "dyn_only", "both")), y = Mean)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.15, alpha = 0.5) +
  labs(x = "Category", y = "KOT (ms)", title = "KOT - Staccato") + scale_y_continuous(breaks = seq(-310, -170, 40)) +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

@@

```{r vel-bl-plot, include = FALSE}
for_ca_plot <- ggplot(vel[Subcomponent2 == "Forte" & Category == "baseline" | Subcomponent2 == "Forte" & Category == "both" | Subcomponent2 == "Forte" & Category == "art_only"], aes(x = factor(Category, level = c("baseline", "art_only", "both")), y = Mean)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.15, alpha = 0.5) +
  labs(x = "Category", y = "KV (0-127)", title = "KV - Forte") + scale_y_continuous(breaks = seq(60, 110, 10)) +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

pia_ca_plot <- ggplot(vel[Subcomponent2 == "Piano" & Category == "baseline" | Subcomponent2 == "Piano" & Category == "both" | Subcomponent2 == "Piano" & Category == "art_only"], aes(x = factor(Category, level = c("baseline", "art_only", "both")), y = Mean)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.15, alpha = 0.5) +
  labs(x = "Category", y = "KV (0-127)", title = "KV - Piano") + scale_y_continuous(breaks = seq(50, 70, 10)) +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

@@

```{r vel-diff-bl-plot, include = FALSE}
ftop_ca_plot <- ggplot(vel_diff[Subcomponent2 == "FtoP" & Category == "baseline" | Subcomponent2 == "FtoP" & Category == "both" | Subcomponent2 == "FtoP" & Category == "art_only"], aes(x = factor(Category, level = c("baseline", "art_only", "both")), y = Mean)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.15, alpha = 0.5) +
  labs(x = "Category", y = "KV Difference (-127-127)", title = "KV Difference - FtoP") + scale_y_continuous(breaks = seq(-35, 0, 10)) +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

ptof_ca_plot <- ggplot(vel_diff[Subcomponent2 == "PtoF" & Category == "baseline" | Subcomponent2 == "PtoF" & Category == "both" | Subcomponent2 == "PtoF" & Category == "art_only"], aes(x = factor(Category, level = c("baseline", "art_only", "both")), y = Mean)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.15, alpha = 0.5) +
  labs(x = "Category", y = "KV Difference (-127-127)", title = "KV Difference - PtoF") + scale_y_continuous(breaks = seq(-5, 45, 10)) +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

>>>>

```{r ioi-plot, include = FALSE}
ioi_all_plot <- ggplot(ioi[Category != "baseline"], aes(x = Articulation, y = Mean, color = Dynamics)) +
  geom_boxplot(outlier.shape = NA, position = position_dodge2(preserve = "single")) +
  geom_hline(yintercept = 300, linetype = "dashed") +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) + labs(y = "IOI (ms)", title = "IOI") + scale_y_continuous(breaks = seq(240, 320, 20), limits = c(240, 320)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

@@

```{r kot-plot, include = FALSE}
leg_all_plot <- ggplot(kot[Subcomponent1 == "Legato" & Category != "baseline"], aes(x = Articulation, y = Mean, color = Dynamics)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KOT (ms)", title = "KOT - Legato") + scale_y_continuous(breaks = seq(-20, 140, 40), limits = c(-20, 140)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

sta_all_plot <- ggplot(kot[Subcomponent1 == "Staccato" & Category != "baseline"], aes(x = Articulation, y = Mean, color = Dynamics)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KOT (ms)", title = "KOT - Staccato") + scale_y_continuous(breaks = seq(-280, -120, 40), limits = c(-280, -120)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

@@

```{r vel-plot, include = FALSE}
for_all_plot <- ggplot(vel[Subcomponent2 == "Forte" & Category != "baseline"], aes(x = Dynamics, y = Mean, color = Articulation)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KV (0-127)", title = "KV - Forte") + scale_y_continuous(breaks = seq(60, 100, 10), limits = c(60, 100)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

pia_all_plot <- ggplot(vel[Subcomponent2 == "Piano" & Category != "baseline"], aes(x = Dynamics, y = Mean, color = Articulation)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KV (0-127)", title = "KV - Piano") + scale_y_continuous(breaks = seq(40, 80, 10), limits = c(40, 80)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

@@

```{r vel-diff-plot, include = FALSE}
ftop_all_plot <- ggplot(vel_diff[Subcomponent2 == "FtoP" & Category != "baseline"], aes(x = Dynamics, y = Mean, color = Articulation)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KV Difference (-127-127)", title = "KV Difference - FtoP") + scale_y_continuous(breaks = seq(-40, 10, 10), limits = c(-40, 10)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

ptof_all_plot <- ggplot(vel_diff[Subcomponent2 == "PtoF" & Category != "baseline"], aes(x = Dynamics, y = Mean, color = Articulation)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KV Difference (-127-127)", title = "KV Difference - PtoP") + scale_y_continuous(breaks = seq(-10, 40, 10), limits = c(-10, 40)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

@@

```{r ioi-bl-plot, include = FALSE}
ioi_ca_plot <- ggplot(ioi[Category == "none" | Category == "both" | Category == "baseline"], aes(x = factor(Category, level = c("baseline", "none", "both")), y = Mean)) +
  geom_boxplot(outlier.shape = NA, position = position_dodge2(preserve = "single")) +
  geom_hline(yintercept = 300, linetype = "dashed") + scale_y_continuous(breaks = seq(200, 380, 20), limits = c(200, 380)) +
  geom_jitter(width = 0.15, alpha = 0.5) + labs(x = "Category", y = "IOI (ms)", title = "IOI") +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

@@

```{r kot-bl-plot, include = FALSE}
leg_ca_plot <- ggplot(kot[Subcomponent1 == "Legato" & Category == "baseline" | Subcomponent1 == "Legato" & Category == "both" | Subcomponent1 == "Legato" & Category == "dyn_only"], aes(x = factor(Category, level = c("baseline", "dyn_only", "both")), y = Mean)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.15, alpha = 0.5) +
  labs(x = "Category", y = "KOT (ms)", title = "KOT - Legato") + scale_y_continuous(breaks = seq(-20, 140, 40), limits = c(-20, 140)) +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

sta_ca_plot <- ggplot(kot[Subcomponent1 == "Staccato" & Category == "baseline" | Subcomponent1 == "Staccato" & Category == "both" | Subcomponent1 == "Staccato" & Category == "dyn_only"], aes(x = factor(Category, level = c("baseline", "dyn_only", "both")), y = Mean)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.15, alpha = 0.5) +
  labs(x = "Category", y = "KOT (ms)", title = "KOT - Staccato") + scale_y_continuous(breaks = seq(-320, -160, 40), limits = c(-320, -160)) +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

@@

```{r vel-bl-plot, include = FALSE}
for_ca_plot <- ggplot(vel[Subcomponent2 == "Forte" & Category == "baseline" | Subcomponent2 == "Forte" & Category == "both" | Subcomponent2 == "Forte" & Category == "art_only"], aes(x = factor(Category, level = c("baseline", "art_only", "both")), y = Mean)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.15, alpha = 0.5) +
  labs(x = "Category", y = "KV (0-127)", title = "KV - Forte") + scale_y_continuous(breaks = seq(60, 100, 10), limits = c(60, 100)) +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

pia_ca_plot <- ggplot(vel[Subcomponent2 == "Piano" & Category == "baseline" | Subcomponent2 == "Piano" & Category == "both" | Subcomponent2 == "Piano" & Category == "art_only"], aes(x = factor(Category, level = c("baseline", "art_only", "both")), y = Mean)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.15, alpha = 0.5) +
  labs(x = "Category", y = "KV (0-127)", title = "KV - Piano") + scale_y_continuous(breaks = seq(40, 80, 10), limits = c(40, 80)) +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

@@

```{r vel-diff-bl-plot, include = FALSE}
ftop_ca_plot <- ggplot(vel_diff[Subcomponent2 == "FtoP" & Category == "baseline" | Subcomponent2 == "FtoP" & Category == "both" | Subcomponent2 == "FtoP" & Category == "art_only"], aes(x = factor(Category, level = c("baseline", "art_only", "both")), y = Mean)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.15, alpha = 0.5) +
  labs(x = "Category", y = "KV Difference (-127-127)", title = "KV Difference - FtoP") + scale_y_continuous(breaks = seq(-40, 10, 10), limits = c(-40, 10)) +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

ptof_ca_plot <- ggplot(vel_diff[Subcomponent2 == "PtoF" & Category == "baseline" | Subcomponent2 == "PtoF" & Category == "both" | Subcomponent2 == "PtoF" & Category == "art_only"], aes(x = factor(Category, level = c("baseline", "art_only", "both")), y = Mean)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.15, alpha = 0.5) +
  labs(x = "Category", y = "KV Difference (-127-127)", title = "KV Difference - PtoF") + scale_y_continuous(breaks = seq(-10, 40, 10), limits = c(-10, 40)) +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")
